Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-27 paper/paper-mainfile.tex

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{xcolor}
\usepackage{booktabs} 
\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{tikz}

@@

From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.

@@

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

@@

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} configured to use to turn the problem into a classical planning problem (in RC model), and Greedy best first search with visited lists. We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). 
We test both Complex and Simple Inference for linearization.

The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
The planner that has achieved the highest overall coverage and IPC score is ? planner.

@@

Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
Figure~\ref{ffig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

\begin{table*}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
			\midrule 
			Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{9.0}  } \\ 
			Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & 15.0 &\multicolumn{2}{c}{ \textbf{16.0}  } \\ 
			Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & 14.0 & \textbf{15.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
			PCP$^{17}$ & 17 & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
			Rover & 20 & 6.0 & \textbf{20.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{19.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
			Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\  
			Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{12.0}  } \\ 
			UM-Translog$^{1}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ \textbf{22.0}  } \\ 
			Woodworking$^{2}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{15.0} & 12.0 & \textbf{20.0} & 9.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
			\midrule 
			Monroe & 100 & 96.0 & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
			SmartPhone$^{1}$ & 7 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
			Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
			\midrule 
			Coverage & 335 & 239.0 & \textbf{287.0} & 188.0 & \textbf{232.0} & 231.0 & \textbf{274.0} & 198.0 &\multicolumn{2}{c}{ \textbf{237.0}  } \\ 
			Norm. coverage & 12 & 8.22 & \textbf{9.95} & 6.85 & \textbf{8.46} & 8.0 & \textbf{9.63} & 7.1 &\multicolumn{2}{c}{ \textbf{8.44}  } \\ 
			\bottomrule 
		\end{tabular}
	}
\end{table*}

\begin{table*}
	\centering
	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleIPC}
	\scalebox{0.85} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
			\midrule 
			Barman-BDI & 1 & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
			Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.56} & 0.45 & \textbf{0.31} & 0.3 & \textbf{0.46} & 0.41 & \textbf{0.22} &\multicolumn{2}{c}{ 0.18  } \\ 
			Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} & 0.25 & \textbf{0.13} & 0.11 & \textbf{0.31} & 0.26 & \textbf{0.17} &\multicolumn{2}{c}{ 0.14  } \\ 
			PCP$^{17}$ & 1 & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ \textbf{0.82}  } \\ 
			Rover & 1 & 0.29 & \textbf{0.95} & 0.14 & \textbf{0.52} & 0.2 & \textbf{0.78} & 0.16 &\multicolumn{2}{c}{ \textbf{0.48}  } \\ 
			Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
			Transport & 1 & 0.24 & \textbf{0.61} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 &\multicolumn{2}{c}{ \textbf{0.2}  } \\ 
			UM-Translog$^{1}$ & 1 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			Woodworking$^{2}$ & 1 & 0.38 & \textbf{0.58} & 0.2 & \textbf{0.41} & 0.36 & \textbf{0.57} & 0.27 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
			\midrule 
			Monroe & 1 & \textbf{0.77} & 0.69 & \textbf{0.5} & 0.47 & \textbf{0.75} & 0.71 & \textbf{0.53} &\multicolumn{2}{c}{ \textbf{0.53}  } \\ 
			SmartPhone$^{1}$ & 1 & \textbf{0.71} & \textbf{0.71} & 0.69 & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} &\multicolumn{2}{c}{ \textbf{0.71}  } \\ 
			Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			\midrule 
			IPC score & 12 & 7.1 & \textbf{8.4} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.9} & 5.8 &\multicolumn{2}{c}{ \textbf{6.7}  } \\
			\bottomrule 
		\end{tabular} 
	}
\end{table*}

>>>>

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{xcolor}
\usepackage{booktabs} 
\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{tikz}
\usetikzlibrary{aiplans}

\scheme{SinglePrec}{0}{
	text = {\textbf{A}},
	pre  = {a}
}

\scheme{SingleAdd}{0}{
	text = {\textbf{B}},
	effs = { a}
}

\scheme{SingleDelete}{0}{
	text = {\textbf{C}},
	effs = { {{$\neg$}a} }
}

\scheme{PrimitiveA}{0}{
	text = {\textbf{A}},
	pre  = {a},
	effs = { {{$\neg$}a}, {b} }
}

\scheme{PrimitiveB}{0}{
	text = {\textbf{B}},
	pre = {b},
	effs = {{{$\neg$}b}, {c}}
}

\scheme{PrimitiveC}{0}{
	text = {\textbf{C}},
	pre = {c},
	eff = {{$\neg$}c}
}

@@

From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
For an visual demonstration of what this algorithm is doing:

 \begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{first}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{second}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\path[every node/.style={font=\sffamily\small}]
			(first) edge [->,bend right] node [left]  {} (second);
			\end{tikzpicture}

			\caption{B adds a fact in preconditions of A -- so B before A}

		\end{subfigure}
	}  
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{B}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{C deletes a fact in preconditions of A  -- so A before C}	
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{B}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->, bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	} 
\end{figure}

\begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{B}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{A}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

			\caption{Resulting method ordering has a cycle}

		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{6cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{B}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{A}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
		%	(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

			\caption{Delete any random ordering to break it}
		\end{subfigure}
	}  
\end{figure}

@@

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

@@

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration. This is when it's configured to turn the problem into a classical planning problem (in RC model), and Greedy best first search, using FF by \cite{FF}, and using visited lists. The visited lists use task sequence hashing, visited checking with task sequences which makes totally-ordered visited lists incomplete (with order), layer hashing, order pairs hashing, no optimisation for parallel sequences,  GI-complete equivalence checking for
partially ordered task networks (with GI-complete checking).

\todo{Most notably, note that TO problems allow for other visited list
	configurations than PO problems. So we should also use a TO
	configuration there (this is however not reported)}

We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. For other planners, panda$_\pi$ with rc2(Add) is used for re-runs. We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). 
We test both Complex and Simple Inference for linearization.

The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.

The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.

For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem. For each total-order planner, the column beneath it shows performance on the linearized problem.
The IPC score has a maximum of 1 per domain, for the 12 domains in total.

@@

Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
\begin{tabular}{lccccccl} 
	\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO\\  
	\midrule 
	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
			\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
			\midrule 
	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleIPC}
	\scalebox{0.85} {
	\begin{tabular}{lccccccccl} 
	\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	& PO & TO & PO & TO  \\ 
	\midrule 
	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\

	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\

	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\

	\midrule 
	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\

	\bottomrule 
		\end{tabular} 		
	}
\end{table}

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.65} {
		\begin{tabular}{lccccccccccl} 
			\toprule 
			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
			&PO & TO & PO & TO  \\ 
			\midrule 
			Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 0.0 & \textbf{17.0}  \\ 
			Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & 0.0 & \textbf{18.0}   \\ 
			Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}   \\ 
			PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 0.0 & 0.0   \\ 
			Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & 0.0 & 20.0   \\ 
			Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 0.0 & \textbf{25.0}   \\ 
			Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 2.0 & \textbf{35.0}   \\ 
			UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 0.0 & \textbf{21.0}   \\ 
			Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
			\midrule
			Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
			SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 0.0 & 1.0  \\ 
			Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & 0.0 & 5.0  \\ 
			\midrule 
			Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{114.0} & \textbf{268.0}  \\ 
			Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & 1.65 & 8.58  \\ 
			\bottomrule 
		\end{tabular}

	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
\begin{tabular}{lccccccccccl} 
	\toprule 
	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
	&PO & TO & PO & TO  \\  
	\midrule 
	Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & 0.0 & \textbf{0.72}  \\

	Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & 0.0 & 0.54   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & 0.63   \\ 
	PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.0 & 0.0   \\ 
	Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & 0.0 & \textbf{0.97}  \\ 
	Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.0 & \textbf{1.0}   \\ 
	Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.22 & 0.78   \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & 0.0 & 0.92   \\ 
	Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.0 & 0.14   \\ 
	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.0 & 1.0   \\ 
	\midrule 
	IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{1.6} & \textbf{7.9}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

\begin{table}
	\centering
	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.7} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-5}   
			&PO & TO & PO & TO \\
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ.$^{2}$   \\ 
			Monroe Part. Observ.$^{2}$  \\ 
			PCP$^{17}$  \\ 
			Rover  \\ 
			Satellite   \\  
			Transport   \\ 
			UM-Translog$^{1}$  \\ 
			Woodworking$^{2}$  \\ 
			\midrule 
			Monroe   \\ 
			SmartPhone$^{1}$   \\ 
			Zenotravel   \\ 
			\midrule 
			Coverage  \\ 
			Norm. coverage  \\ 
			\bottomrule 
		\end{tabular}  
	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.7} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
 &PO & TO & PO & TO \\
\midrule 
Barman-BDI  \\ 
Monroe Fully Observ.$^{2}$   \\ 
Monroe Part. Observ.$^{2}$  \\ 
PCP$^{17}$  \\ 
Rover  \\ 
Satellite   \\  
Transport   \\ 
UM-Translog$^{1}$  \\ 
Woodworking$^{2}$  \\ 
\midrule 
Monroe   \\ 
SmartPhone$^{1}$   \\ 
Zenotravel   \\ 
\midrule 
IPC score \\
\bottomrule 
\end{tabular}  
	}
\end{table}
